Selección de Servicios Web De Máxima Utilidad Usando Circuitos

### 2009-12-13 tesis/propuesta/planteamiento.tex
separacion de partes de la propuesta en .texs

  \documentclass{llncs}
\usepackage{amsmath}
\usepackage{txfonts}
\usepackage[boxed]{algorithm2e}
\usepackage{amssymb}
\usepackage[pdftex]{graphicx}
\usepackage[utf8x]{inputenc}
\usepackage{enumerate}
\DeclareGraphicsExtensions{.jpg, .png, .mps, .bmp, .pdf}
\usepackage{epsfig}
\usepackage{subfigure}
\newtheorem{Definition}{Definition} 
\newtheorem{Example}{Example} 
\newtheorem{Theorem}{Theorem} 
\newtheorem{Proof}{Proof} 
\newcommand{\denselist}{\topsep 0pt \itemsep -4pt}
\newcommand{\tup}[1]{\langle #1 \rangle}
\newcommand{\vvec}[1]{\mathbf{#1}}
\newcommand{\join}{\bowtie}
\newcommand{\R}{\mathcal{R}}
\newcommand{\Q}{\mathcal{Q}}
\newcommand{\body}{{body}}
\newcommand{\head}{{head}}
\newcommand{\qrule}{:\!\!-}
\newcommand{\arc}{\text{arc}}
\newcommand{\Theory}[1]{T(#1)}
\newcommand{\mcdsat}{\textsc{McdSat}}
\newcommand{\minicon}{{MiniCon}}
\newcommand{\Omit}[1]{}
\newcommand{\citeX}[1]{\citeauthor{#1}~\citeyear{#1}}

\begin{document}
\allowdisplaybreaks
\title{Selección de Servicios Web De Máxima Utilidad Usando Circuitos}
\author{Daniel Izquierdo}

\institute{Universidad Sim\'on Bol\'{\i}var\\
                Caracas, Venezuela\\
                idaniel@ldc.usb.ve} \maketitle
\begin{abstract}
En las arquitecturas orientadas a servicios (SOA), los servicios concretos se
describen en términos de parámetros de funcionalidad y calidad de servicio,
mientras que las aplicaciones de \emph{software} se especifican como flujos de
trabajo de servicios abstractos y criterios no-funcionales que establecen la
funcionalidad deseada y la calidad esperada respectivamente. En tiempo de
ejecución de un flujo de trabajo, los servicios abstractos se reescriben con los
servicios concretos que cumplen con las restricciones funcionales y no
funcionales del flujo de trabajo. Dado que la selección de los servicios es
hecha al momento y el espacio de servicios concretos puede ser muy grande, se
requiere eficiencia y escalabilidad. En este trabajo se propone la
infraestructura {\it McdSat}$^c$ para resolver eficientemente el problema de
selección de servicios en presencia de un número grande de servicios concretos.
En primer lugar se utiliza la aproximación \emph{Local As View} para describir
la funcionalidad de los servicios concretos en términos de vistas de servicios
abstractos, la calidad como una función de utilidad general que combina los
distintos valores de calidad que describen cada servicio, y los flujos de
trabajo como consultas conjuntivas sobre servicios abstractos. Basándose en esta
representación, se modela el problema de selección de servicios como un problema
conocido en el área de integración de sistemas conocido como reescritura de
consultas usando vistas. Codificamos el problema de selección de servicios como
una teoría proposicional cuyos modelos corresponden a la composición de los
servicios que implementan el flujo abstracto; se explotan relaciones conocidas
entre teorías d-DNNF y circuitos aritméticos para proveer una solución eficiente
y escalable. Se reporta sobre el rendimiento de la aproximación propuesta y se
observa que  {\it McdSat}$^c$  escala a instancias grandes del problema de
selección de servicios.

\end{abstract}

\section{Introducción}
Bajo la sombra de la Web Semántica y con el apoyo de arquitecturas orientadas a
servicios, el número de fuentes de datos y servicios Web ha explotado en los
últimos años. Por ejemplo, actualmente la colección de bases de datos de
biología molecular incluye 1.170 bases de datos~\cite{Galperin09}, lo cual es 95
más que el año pasado~\cite{Galperin2008} y 110 más que hace dos
años~\cite{Galperin2007}. Tanto las herramientas y servicios como el número de
instancias publicadas por estos recursos siguen una progresión
similar~\cite{Benson07}. Gracias a este tesoro de datos, los usuarios se apoyan
más en varias tareas digitales como obtención de datos de fuentes públicas y
análisis de datos con herramientas o servicios Web organizados en flujos de
trabajo complejos.

Para diseñar una aplicación, los usuarios frecuentemente especifican la
funcionalidad en términos de un flujo de trabajo de servicios abstractos,
mientras que la calidad deseada se define restringiendo los valores de los
parámetros QoS (calidad de servicio) que describen los servicios concretos
disponibles. Para evaluar el flujo propuesto, se instancian los servicios
abstractos con concretos de manera que se satisfagan las restricciones sobre
parámetros QoS. Sin embargo, el rendimiento de estas tareas es impactado por el
número de fuentes disponibles. Se requieren técnicas que permitan escalar
eficientemente a un número grande de servicios.

En este trabajo se intenta proponer una solución a este problema y proveer
técnicas que recorran eficientemente el espacio de servicios disponibles y
seleccionen combinaciones que cumplan con los requerimientos funcionales y
no-funcionales que describen una aplicación diseñada. Se llama 
{\it MCDSat}$^c$ a la solución propuesta.

En {\it MCDSat}$^c$, las funcionalidades de servicios concretos se describen
como vistas sobre servicios abstractos y los flujos de trabajo se representan
como consultas conjuntivas sobre servicios abstractos; esta representación de
los servicios es similar a la generada de manera semiautomática para el
sistema {\cal DEIMOS}~\cite{AmbiteISWC09}. Adicionalmente, las reglas
que definen flujos de trabajo y servicios concretos en el catálogo de
{\it MCDSat}$^c$ son creadas de manera que las restricciones de entrada y salida
de los servicios abstractos combinados sean satisfechas. Para representar las
medidas de QoS, cada descripción de servicio concreto es anotada con un número
real que representa un valor general para las medidas de QoS del servicio en
particular. Finalmente, {\it MCDSat}$^c$ modela el problema de selección de
servicios web como el problema de reescritura de consultas usando vistas
\cite{halevy:survey}. Este problema es importante en el contexto de integración
de datos \cite{Chen05,JaudoinPRST05} y de optimización de consultas y
mantenimiento de datos \cite{AfratiLU07,levy:bucket} y se han definido varias
aproximaciones para escalar eficientemente a un número grande de
vistas~\cite{arvelo:aaai06,pods:DuschkaG97,sac:DuschkaG97,levy:bucket,pottinger:minicon}.
En este trabajo se propone la infraestructura {\it MCDSat}$^c$ que extiende la
aproximación propuesta en  ~\cite{arvelo:aaai06}, con la capacidad de trabajar
con constantes y de identificar la composición de servicios que maximice una
función de utilidad dada.

{\it MCDSat}$^c$  traduce una instancia del problema de selección de servicios
en el problema de enumerar los modelos de una teoría proposicional que codifica
información sobre el flujo de trabajo, los servicios concretos y las condiciones
que deben ser satisfechas para generar una composición que maximice la función
de utilidad. Esta teoría se representa como una fórmula CNF que es compilada a
su representación d-DNNF, a partir de la cual los modelos que maximicen la
función global de utilidad se obtienen en tiempo lineal usando técnicas modernas
de SAT~\cite{darwiche:dnnf}. Se estudia empíricamente la calidad de {\it
MCDSat}$^c$ sobre una variedad de \emph{benchmarks} y se observa que la técnica
propuesta provee una solución eficiente al problema de selección de servicios
que es capaz de escalar a flujos de trabajo grandes así como a números de vistas
grandes.

This paper is comprised of six additional sections. The next section motivates our approach by using an example, and  we summarize existing related work in section 3. Section 4 describes the {\it MCDSat}$^c$ system architecture, and  the experimental study is reported in section 5. 
In section 6 we present the formalization of the web service selection problem as a Propositional Logic theory, and finally, section 7 outlines our conclusions and future work.

@@

La composición {\it wi2} no es válida porque asocia la variable del flujo de
trabajo {\it y2} a las constantes {\it "CCS"} y {\it "WAS"} que denotan ciudades
distintas. Por otra parte, la composición {\it wi3} no implementa el flujo de
trabajo porque el servicio concreto {\it onestop} no recibe como entrada o
produce como salida la ciudad donde el vuelo se detiene (representada por la
variable {\it y1}); por esto, no es posible garantizar que la ciudad donde el
vuelo se detiene y la ciudad final obtenida por el servicio {\it national} sean
las mismas.

@@

\section{Related Work}
In this section we summarize existing approaches that provide solutions to the problems of service selection, knowledge representation and query rewriting.

\begin{description}
\item[Service Selection Solutions] \mbox{}\\
The problem of selecting the services that implement an abstract workflow and best meet the QoS-based criteria  is known as the QoS-aware service selection or composition problem, which has been shown to be NP-hard~\cite{Hiroshi2008}. This problem is a combinatorial optimization problem and several heuristics have been proposed to find a relatively good solution in a reasonably short period of time.  A  distance metric-based heuristic  to drive a backward search algorithm  is proposed~\cite{rahmani08}; this metric induces an order of the services in a way that sink nodes are unlikely to be visited. In ~\cite{berardi05,berardi08,berardi06}, services and workflows are described in terms of deterministic finite state machines that are encoded as a Description Logic theory whose models correspond to solutions of the problem;  although reasoning methods for Description Logics formalisms could be exploited, scalability or performance of the proposed solution has not been reported.  ~\cite{myoung08} propose a constraint-based approach that encodes the non-functional permissible values as a set of constraints whose violation needs to be minimized; to traverse the space of possibly optimal solutions, a hybrid algorithm that combines the tabu search and simulating annealing meta-heuristics is implemented; experimental results show that the proposed solution is able to scale up to a large number of services and abstract processes.  In ~\cite{cardellini07} the QoS-aware service composition problem is encoded as a Linear Programming problem providing a scalable solution to the problem.  In ~\cite{Hiroshi2008}  this problem  is defined as a multi-objective optimization problem where the different QoS parameters are considered equally important and there is not an aggregated function to combine all of them; a genetic-based algorithm is proposed to identify a set of non-dominated service compositions that best meet all the QoS parameters.  ~\cite{alrifaiR09} propose a two-fold solution that uses a hybrid integer programming algorithm to find the decomposition of global QoS into local constraint, and then,  selects the services that best meet the local constraints.   
Recently,  two new planning-based approaches have been proposed~\cite{kuterG09,sohrabiM09}.  ~\cite{kuterG09} extend the SHOP2 planning algorithm to select the trustworthy composition of services that implement a given OWL-S process model, while ~\cite{sohrabiM09}  propose a HTN planning-based solution where user preference metrics and domain regulations are used to guide the planner into the space of relevant compositions. Finally, ~\cite{lecue09} proposes a genetic-based algorithm to identify the composition of services that best meet the quality criteria for a set of QoS parameters.

Although these solutions are able to efficiently solve the optimization problem and scale up to a large number of abstract processes, none of them are tailored to semantically describe services in terms of the abstract process, or use these descriptions to identify the services that  implement a given workflow and best meet user non-functional criteria.

\item[Knowledge Compilation Languages] \mbox{}\\
Knowledge compilation is the area in AI concerned with the
problem of mapping logical theories into suitable fragments
that make certain desired operations tractable
\cite{cadoli:compilation}. Different compilation languages have been defined, for instance,  
Ordered Binary Decision Diagrams (OBDDs)~\cite{bryant:obdd},  Negation Normal Form (NNF) \cite{barwise:handbook}, and Decomposable Negation Normal Form (DNNF)  \cite{darwiche:dnnf}.
In this work we make use of the properties of the deterministic DNNFs  (d-DNNF) \cite{darwiche:d-dnnfs} to provide an scalable and efficient solution to the service selection problem.

A Negation Normal Form (NNF) theory is  constructed from literals using only conjunctions
and disjunctions \cite{barwise:handbook}, and it can be represented as a directed acyclic graph
in which the leaves are labeled with literals and the
internal nodes are labeled with $\land$ and $\lor$;
see Fig.~\ref{fig:dnnf} for an example. An NNF is said to be decomposable (DNNF) \cite{darwiche:dnnf}
if for each conjunction $\bigwedge_i\phi_i$, the set of
variables in each conjunct are pairwise disjoint;
i.e,. $Vars(\phi_i)\cap Vars(\phi_j)=\empty$ for $i<j$.
A DNNF supports a number of operations in
polynomial time in the size of its DAG. For example,
we can test whether a DNNF is satisfiable by a single
bottom-up pass over its DAG in linear time. A DNNF is said to be deterministic (d-DNNF) \cite{darwiche:d-dnnfs} if for each disjunction $\bigvee_i\phi_i$, the disjuncts
are pairwise logically contradictory; i.e.,
$\phi_i\Rightarrow\neg\phi_j$ for $i<j$.
The NNF in Fig.~\ref{fig:dnnf}, for example, is decomposable
and deterministic. A d-DNNF supports the model counting and enumeration in polynomial time
in the size of its DAG.  {\it MCDSat}$^c$  exploits the properties of a d-DNNF theory, to efficiently provide a solution to the problem of enumerating the service compositions that correspond to models of the  theory, i.e., the service compositions that implement the abstract  workflow and best meet the utility function. DECIR ALGO SOBRE EL ALGORITMO QUE PRODUCE LOS MEJORES.

\begin{figure}
\centering
%\includegraphics[width=8cm]{odd}
\caption{A decomposable and deterministic NNF.}
\label{fig:dnnf}
\end{figure}

\item[Query Rewriting Solutions] \mbox{}\\
A number of algorithms have been developed to find the rewritings of a given query; the most prominent being the bucket algorithm~\cite{levy:bucket},  the inverse rules algorithm ~\cite{duschka:answer,Qian96}, the minicon algorithm ~\cite{pottinger:minicon}, and the {\it MCDSat} ~\cite{arvelo:aaai06}. Generally, query rewriting algorithms work in two phases: first, they identify the views that rewrite at least one  subgoal of the query; second they combine the selected views to produce a rewriting. The main difference between existing approaches, is the criteria used to choose the relevant views and reduce the space of non-useful rewritings.

The bucket algorithm reduces the number of possibilities just considering each subgoal in the query in isolation, and selecting the views that are able to  produce at least the attributes projected by the query. Since, attributes involved in query joins are not verified, a large number of rewritings comprised of  Cartesian products may  be generated. 	
The Inverse Rules algorithm constructs a set of rules that invert the view definition and establish how to compute tuples for the database relations from tuples of the views. Similarly, to the bucket algorith it can produce a large number non-useful of rewritings.

The MiniCon algorithm  overcomes the limitations of the previous algorithms by identifying only views that rewrite a set of the query goals and that  can be combined with the rest of the query subgoals. The key idea is to identify the mappings between  the variables in each subgoal of the query to the variables  in one or more subgoals of the views, in a way that, join variables in the query are mapped to join variables in the body of a view or to the distinguished variables of the view. Mappings between variables and subgoals are represented in MiniCon Descriptions (MCD's)\cite{pottinger:minicon}.

Finally,  the
{\it MCDSat} algorithm is able to identify the query rewritings of a query by translating the problem of rewriting
into the problem of enumerating the models of a propositional
theory  $\Theory{\Q}$ whose models are in correspondence
with the rewritings of the query. 
The {\it MCDSat} algorithm exploits the properties of d-DNNFs to efficiently 
compute the MCDs associated with theory $\Theory{\Q}$.
The  {\it MCDSat} algorithm has demonstrated to scale better than the MiniCon
algorithm over a large number of benchmarks often showing performance
improvements of several orders of magnitude. However, the McdSat algorithm was not desgined for rewriting problems involving explicit constants,
nor to compute the best rewritings with respect to a given utility function or cost model, and this paper we propose a new encoding  that overcomes these limitations.

\end{description}

\section{The McdSat$^c$ Architecture}

In order to do so, the theory $\Theory{\Q}$ is transformed into a d-DNNF
theory $\Delta(\Q)$ with a CNF to d-DNNF compiler.
The compiler's algorithm is similar to the DPLL algorithm
for SAT but enhanced with advanced techniques such as clause
learning and caching.
\begin{figure}
\centering
%COMENTADO\includegraphics[width=10cm]{mdcsatC.pdf}
\caption{The McdSat$^c$ Architecture}
\label{fig:dnnf}
\end{figure}

\section{Experimental Results}
We have conducted an empirical analysis  on the benefits of the techniques implemented in the   McdSat$^c$ system.

\begin{description}
\item[Dataset and Query Benchmark:]  we conducted our experiments over a benchmark that includes XX queries and a set of  YY views. Queries and views are starts and chains, and they have between ZZ and fTT constants; queries have QQ sub-subgoals.
\item[Evaluation Metrics:] we report on runtime performance which corresponds to the  {\it user time} produced by the {\it time} command of the Unix operation system. 
\end{description}

\begin{figure}
\centering
%COMENTADO\includegraphics[width=8cm]{plot1.pdf}
\caption{Compilation Time Benchmark I}
\label{fig:plot1}
\end{figure}

\section{Formalization of the Service Selection Problem}

We consider databases of the form $D=\tup{P,T}$ where
$P$ is a set of predicates and $T=\{T_p\}_{p\in P}$ is a collection
of tables that represents the predicates in extensional form.
A conjunctive query $Q$ over $P$ is of the form 
\begin{alignat*}{1}
Q(\vvec{x})\ \qrule\ \  p_1(\vvec{x}_1),\, p_1(\vvec{x}_2),\, \ldots,\, p_m(\vvec{x}_m)\,,
\end{alignat*}
where $p_i\in P$, $\vvec{x}$ is a vector of variables, and each
$\vvec{x}_i$ is a vector of variables and constants.
The result of $Q$ over $D$, denoted as $Q(D)$, is the table with
$|\vvec{x}|$ columns that result of the projection of the relational
join $\join\!\!\{T_{p_i}\}_{i=1}^m$ over $\vvec{x}$.
The atoms in the body of $Q$ are called the (sub)goals of $Q$.

A view $V$ over $D$ is a query over $P$. In the context of the service selection problem, 
the database $D$ is an idealized description of 
the output produced abstract workflow  implemented by multiple concrete services described
as views.
Given a database $D$, a query $Q$ and a collection of 
views $E=\tup{\{V_i\}_i,\{E_i\}_i}$, we are required to find
all the tuples in $Q(D)$ obtainable from the views in $E$.
That is, we need to find all the \emph{compositions} of the form
\begin{alignat*}{1}
R(\vvec{x})\ \qrule\ \ V_{i_1}(\vvec{x}_1),\, V_{i_2}(\vvec{x}_2),\, \ldots,\, V_{i_n}(\vvec{x}_n)
\end{alignat*}
such that $R(E) \subseteq Q(D)$.
A service selection problem (SSP) is a tuple $\tup{P,Q,\{V_i\}}$ where $P$
is a set of predicates that represent abstract services, $Q$ is a query over $P$ and $\{V_i\}$ is a collection of views that define the concrete services in terms of  abstract services. We assume \emph{safe} problems in the sense that all 
variables mentioned in the head of the query (resp.\ in the head of each view)
appear in the body of the query (resp.,\ in the body of each view); also the input and output restrictions of the abstract services used in the query are satisfied.
Further, we only deal with SSPs with no arithmetic predicates inside the
query or views.
A composition $C$ is \emph{valid} if for all databases $D=\tup{P,T}$
and extensions $\{E_i\}$, $R(E) \subseteq Q(D)$.
A collection $\R$ of valid compositions is a solution if
for all databases $D=\tup{P,T}$ and extensions $\{E_i\}$, there
is no other $\R'$ such that $\R(E)\subset\R'(E)\subseteq Q(D)$.
We are interested in finding a composition $\R$.

\subsection{Logical Theories}

In \cite{arvelo:aaai06}, we showed that a rewriting
for a query $Q$ with $m$ goals can be obtained by enumerating the
models of a logical theory
$\Delta=\Delta_{rew}\cup\Delta_{mcd}^1\cup\cdots\Delta_{mcd}^m$
where $\Delta_{rew}$ specified how to combine $m$ independent
copies of MCD theories $\Delta_{mcd}$ that cover all goals in $Q$.
Each $\Delta^i_{mcd}$ is a copy of the theory $\Delta_{mcd}$
in which each literal $p$ is tagged as $p^i$.
The theory $\Delta_{mcd}$ consists of different groups of 
clauses that guarantees that its models are in correspondence
with the MCDs, while the theory $\Delta_{rew}$ contains additional
clauses to guarantee a sound and complete composition of the MCDs.
The reader is referred to \cite{arvelo:aaai06} for a comprehensive
description of the propositional theory.

Let us describe the difficulties that arise when constants
are presents in a SSP with the following example:
\begin{alignat*}{1}
Q(x,z)\ &\qrule\ \ p_1(x,y),\, p_2(y,z)\,, \\
V_1(x_1)\ &\qrule\ \ p_1(x_1,A)\,, \\
V_2(x_2)\ &\qrule\ \ p_2(B,x_2)\,, \\
V_3(x_3,y_3)\ &\qrule\ \ p_2(x_3,y_3)
%V_4(x_4,y_4)\ &\qrule\ \ p_1(x_1,A),\, p_2(B,y_4)\,,
\end{alignat*}
where $Q$ is the query and $\{V_1,V_2,V_3\}$ are the 
views. In this case, the only rewriting is 
$R(x,z)\qrule V_1(x),V_3(A,z)$ because the candidate 
$R(x,z)\qrule V_1(x),V_2(z)$ is not valid as it maps
$y$ into constants $A$ and $B$ that denote different
objects.

The main problem when handling constants is to
be sure that different constants are not mapped into
each other either directly or indirectly (via transitivity).

\subsection{Utility Functions}

We assume a simple additive utility function in which each view
$V_i$ is associated with a utility measure $c(V_i)$, and the overall utility value of
a composition is the sum of the utility values for the views in it.
An optimal or best service composition is one with maximum utility value,
and the optimal utility value of a SSP is the utility value of a best
service composition. A SSP has always a well-defined optimal
utility value (if there are no compositions, its utility is $0$),
but it may have multiple best service compositions.
The service composition problem with utility consists in finding
all the compositions of maximum utility value.

%The cost model is simple yet expressive; e.g., if all
%costs are unit, then best rewritings are those with
%minimum number of views, yet in cases where views
%represent different sources, it is natural
%to associate them with different costs.

\subsection{Extended Theories}

The theory $\Delta_{mcd}$ makes use of propositions $t_{x,y}$
to denote that the variable/constant $x$ in the query is mapped
into the variable/constant $y$ in the view, and propositions $v_i$
to indicate that the MCD uses view $V_i$.
We obtain a sound and complete theory for SSPs with constants if
$\Delta_{mcd}$ is extended with the clauses:

\begin{enumerate}[C1.]\denselist
\item (Inconsistent-1): $t_{x,A} \Rightarrow \neg t_{x,B}$,
\item (Inconsistent-2): $t_{A,x} \Rightarrow \neg t_{B,x}$,
\item (Inconsistent-3): $\neg t_{A,B}$,
\item (Transitivity-1): $v_i\land t_{A,y}\land t_{x,y}\land t_{x,z}\Rightarrow t_{A,z}$,
\item (Transitivity-2): $v_i\land t_{y,A}\land t_{y,x}\land t_{z,x}\Rightarrow t_{z,A}$.
\end{enumerate}
Clauses C1--C3 prune candidate service compositions in which one constant
is directly mapped into a different one, and the last two implement
a restricted propagation of transitivity.
Similarly, $\Delta_{rew}$ must be extended with the clauses:
\begin{enumerate}[C1.]\denselist
\item[C6.] (Inconsistent-4): $t^i_{x,A} \Rightarrow \neg t^j_{x,B}$.
\end{enumerate}
~\cite{RajaramanSU95} showed that for queries without negation or arithmetic comparisons,  but with constants, and $m$ goals and $q$ variables, it is enough
to consider service compositions of length at most  $m$ plus  $q$ subgoals ~\cite{Ullman00}.

Given a SSP problem $\tup{Q,\{V_i\}}$ possibly with constant 
symbols, we construct logical theories whose models are in
correspondence with the service compositions. These theories are then
compiled into d-DNNF from which all rewritings are extracted
efficiently.
Likewise, best service compositions can be computed by performing model
enumeration twice: the first pass computes the optimal utility function,
and the second filters out suboptimal service compositions.
However, there is a better way, which we will describe in the next section.

\subsection{Maximum-Utility Function}

Darwiche \& Marquis \cite{darwiche:weighted} show how to compute the
rank $r^*(\Delta)$ of a propositional theory $\Delta$
efficiently when $r$ is a literal ranking function and
$\Delta$ is in d-DNNF. A literal ranking function ranks
the models of the theory in terms of the rank of the
literals $l$ that are true in the model, and ranks the
theory as the best rank of its models:
\[ r(\omega) = \sum_{\omega\vDash l} r(l),\quad r^*(\Delta) = \max_{\omega\vDash\Delta} r(\omega)\,. \]
Furthermore, not only $r^*(\Delta)$ can be computed
efficiently from the d-DNNF but also the models that
have such rank.
The procedure for computing the rank converts the d-DNNF
into a circuit in which the literals are replaced by their
ranks, the `or' nodes by `max', and the `and' nodes by `sum'.
The evaluation of the circuit computes the rank of $\Delta$.

We thus obtain a simple method for computing the best
rewritings when the literal ranking function $r_c$ induced
by the cost model $c$ is used; $r_c$ is defined by
$r_c(l)=c(V_i)$ if $l=v^t_i$ for some $t$, and $r_c(l)=0$
otherwise.

\section{Conclusions and Future Work}

compute the best rewritings with respect to an additive
cost model. The cost model is simple yet expressive.
The computation of the best models relies on an arithmetic
circuit that is obtained from the d-DNNF of the propositional
theory.

\bibliographystyle{abbrv}
\bibliography{ref}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% PARTE DEL FORMATO
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% TODO PORTADA

% TODO indice

\section{Planteamiento del problema}
\section{Justificación e importancia}
\section{Objetivos}
\section{Metodología propuesta}
\section{Cronograma de actividades}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Referencias
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\addcontentsline{toc}{section}{Referencias} 
\bibliographystyle{abbrv}
\bibliography{ref}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% FIN PARTE DEL FORMATO
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\end{document}

>>>>

\section{Planteamiento del problema}

Bajo la sombra de la Web Semántica y con el apoyo de arquitecturas orientadas a
servicios, el número de fuentes de datos y servicios Web ha explotado en los
últimos años. Por ejemplo, actualmente la colección de bases de datos de
biología molecular incluye 1.170 bases de datos~\cite{Galperin09}, lo cual es 95
más que el año pasado~\cite{Galperin2008} y 110 más que hace dos
años~\cite{Galperin2007}. Tanto las herramientas y servicios como el número de
instancias publicadas por estos recursos siguen una progresión
similar~\cite{Benson07}. Gracias a este tesoro de datos, los usuarios se apoyan
más en varias tareas digitales como obtención de datos de fuentes públicas y
análisis de datos con herramientas o servicios Web organizados en flujos de
trabajo complejos.

Para diseñar una aplicación, los usuarios frecuentemente especifican la
funcionalidad en términos de un flujo de trabajo de servicios abstractos,
mientras que la calidad deseada se define restringiendo los valores de los
parámetros QoS (calidad de servicio) que describen los servicios concretos
disponibles. Para evaluar el flujo propuesto, se instancian los servicios
abstractos con concretos de manera que se satisfagan las restricciones sobre los
parámetros QoS. Sin embargo, el rendimiento de estas tareas es impactado por el
número de fuentes disponibles. Se requieren técnicas que permitan escalar
eficientemente a un número grande de servicios.

En este trabajo se intenta proponer una solución a este problema y proveer
técnicas que recorran eficientemente el espacio de servicios disponibles y
seleccionen combinaciones que cumplan con los requerimientos funcionales y
no-funcionales que describen una aplicación diseñada. Se llama 
\mcdsatc a la solución propuesta.

En \mcdsatc, las funcionalidades de servicios concretos se describen
como vistas sobre servicios abstractos y los flujos de trabajo se representan
como consultas conjuntivas sobre servicios abstractos; esta representación de
los servicios es similar a la generada de manera semiautomática para el
sistema {\cal DEIMOS}~\cite{AmbiteISWC09}. Adicionalmente, las reglas
que definen flujos de trabajo y servicios concretos en el catálogo de
\mcdsatc son creadas de manera que las restricciones de entrada y salida
de los servicios abstractos combinados sean satisfechas. Para representar las
medidas de QoS, cada descripción de servicio concreto es anotada con un número
real que representa un valor general para las medidas de QoS del servicio en
particular. Finalmente, \mcdsatc modela el problema de selección de
servicios web como el problema de reescritura de consultas usando vistas
\cite{halevy:survey}. Este problema es importante en el contexto de integración
de datos \cite{Chen05,JaudoinPRST05} y de optimización de consultas y
mantenimiento de datos \cite{AfratiLU07,levy:bucket} y se han definido varias
aproximaciones para escalar eficientemente a un número grande de
vistas~\cite{arvelo:aaai06,pods:DuschkaG97,sac:DuschkaG97,levy:bucket,pottinger:minicon}.
En este trabajo se propone la infraestructura \mcdsatc que extiende la
aproximación propuesta en  ~\cite{arvelo:aaai06}, con la capacidad de trabajar
con constantes y de identificar la composición de servicios que maximice una
función de utilidad dada.

\mcdsatc  traduce una instancia del problema de selección de servicios
en el problema de enumerar los modelos de una teoría proposicional que codifica
información sobre el flujo de trabajo, los servicios concretos y las condiciones
que deben ser satisfechas para generar una composición que maximice la función
de utilidad. Esta teoría se representa como una fórmula CNF que es compilada a
su representación d-DNNF, a partir de la cual los modelos que maximicen la
función global de utilidad se obtienen en tiempo lineal usando técnicas modernas
de SAT~\cite{darwiche:dnnf}. Se estudia empíricamente la calidad de \mcdsatc
sobre una variedad de \emph{benchmarks} y se observa que la técnica
propuesta provee una solución eficiente al problema de selección de servicios
que es capaz de escalar a flujos de trabajo grandes así como a números de vistas
grandes.

This paper is comprised of six additional sections. The next section motivates
our approach by using an example, and  we summarize existing related work in
section 3. Section 4 describes the \mcdsatc system architecture, and  the experimental study is reported in section 5. 
In section 6 we present the formalization of the web service selection problem as a Propositional Logic theory, and finally, section 7 outlines our conclusions and future work.

@@

La composición {\it wi2} no es válida porque asocia la variable del flujo de
trabajo {\it y2} a las constantes {\it ``CCS''} y {\it ``WAS''} que denotan
ciudades
distintas. Por otra parte, la composición {\it wi3} no implementa el flujo de
trabajo porque el servicio concreto {\it onestop} no recibe como entrada o
produce como salida la ciudad donde el vuelo se detiene (representada por la
variable {\it y1}); por esto, no es posible garantizar que la ciudad donde el
vuelo se detiene y la ciudad final obtenida por el servicio {\it national} sean
las mismas.

@@
